\newgeometry{left=3cm,right=3cm}
\begin{thebibliography}{1}

\bibitem{cloud_computing}
Mell, P. and Grance, T. (2011). \emph{The NIST Definition of Cloud Computing}. 1st ed. [ebook] pp.2-3. Available at: \url{http://faculty.winthrop.edu/domanm/csci411/Handouts/NIST.pdf} [Accessed 5 Oct. 2016].

\bibitem{waf}
Lu M, Wing-lok Yeung. \emph{A framework for effective commercial Web application development}. Internet Research 1998;8(2):166-173.

\bibitem{symfony_guide}
Zaninotto, F. and Potencier, F. (2007). \emph{The definitive guide to symfony}. Berkeley, Calif.: Apress.

\bibitem{symfony_pdf}
Jarmolowicz, J., Zabierowski, W. and Napieralski, A. (2016). \emph{Presentation of improvements for PHP}. 1st ed. [ebook] p.1. Available at: \url{https://www.researchgate.net/profile/Wojciech_Zabierowski/publication/251883714_Presentation_of_improvements_for_PHP_programmers_based_on_Symfony_framework._Creation_of_example_portal_and_description_of_used_technology/links/00b7d538f112357a92000000.pdf} [Accessed 3 Oct. 2016].

\bibitem{elderly_cost}
Karlsson, M., Mayhew, L., Plumb, R. and Rickayzen, B. (2016). 2006. 1st ed. [ebook] London, UK: City University, p.198. Available at: \url{http://www.actuaries.org/IAAHS/OnlineJournal/2006-2/long\%20term\%20care\%20UK.pdf} [Accessed 5 Oct. 2016].

\bibitem{IoT}
Gubbi, J., Buyya, R., Marusic, S. and Palaniswamia, M. (2016). \emph{Internet of Things (IoT): A Vision, Architectural Elements, and Future Directions}. 1st ed. [ebook] Melbourne, p.1. Available at: \url{https://arxiv.org/pdf/1207.0203.pdf} [Accessed 5 Oct. 2016].

\bibitem{Tanenbaum}
Tanenbaum, A. and Steen, M. (2007). \emph{Distributed systems}. Upper Saddle River, NJ: Pearson Prentice Hall.

\bibitem{ZeroMQ-book}
Hintjens, P. (2013). \emph{Code connected}. [S.l.]: [s.n.].


\end{thebibliography}